Bioverse: Origins of Life

### 2023-11-01 src/tex/ms.tex
add glossary for acronyms, own section for Conclusions

\subsection{Considered planets and their orbits}
All Origins of Life scenarios considered here require water as a solvent; we thus consider only rocky planets that may sustain liquid water on their surface.
Different formulations of habitable zones as regions around a star where a planet with Earth's atmospheric composition can maintain liquid water on its surface exist~\citep[e.g.,][]{MolLous2022,Spinelli2023,Tuchow2023}. CITE! Ramirez \& Kaltenegger 2017, 2018
Here, we adopt the popular estimates of \citet{Kasting1993} and \citet{Kopparapu2013,Kopparapu2014} that define a temperate zone between the runaway greenhouse transition CITE! and the maximum greenhouse limit CITE!.
We use the parametrization in \citet{Kopparapu2014} to derive luminosity and planetary mass-dependent edges of the habitable zone $a_\mathrm{inner}$ and $a_\mathrm{outer}$.
We further follow \citet{Bixel2021} and classify as ``exo-Earth candidates'' all planets with radii $0.8 S^{0.25} < R < 1.4 $ that orbit within the above boundaries.
The lower limit was suggested as a minimum planet size to retain an atmosphere~\citep{Zahnle2017}.

@@

\subsection{H3: Life only originates on planets with particular UV irradiance}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions:uv}) by relating the occurrence of life on an exo-earth candidate with a minimum past quiescent stellar UV flux, focusing on the prebiotically interesting NUV range from \SIrange{200}{280}{\nano\meter}. \todo[inline]{SUKRIT: got a good reference for this?}  %~\citep{RanjanSasselov2016}.?
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received such radiation exceeded a minimum flux $F_\mathrm{NUV, min}$.
We further require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}, and the planet to be within its momentary habitable zone during this entire period.

For each exo-earth candidate, we interpolated the age- and stellar mass-dependent habitable zone fluxes obtained by \citet{Richey-Yowell2023} and computed the evolution of the inner (runaway greenhouse) and outer (maximum greenhouse) edges as a function of planet mass, stellar spectral type using the results of \citet{Kopparapu2014} and the stellar luminosity evolution of \citet{Baraffe1998}.
We then determined which planets were both in the HZ and had NUV fluxes above $F_\mathrm{NUV, min}$ for $\Delta T_\mathrm{min} \geq \SI{100}{\mega\year}$.
We assigned the development of life to a fraction $f_\mathrm{life}$ of all temperate planets fulfilling these requirements.
For a population-level hypothesis, we then have
\begin{equation}\label{eq:hypothesis-uv}
    H_{3} = f_\mathrm{life} (\theta, F_\mathrm{NUV}) =
        \begin{cases}
            0 , & F_\mathrm{NUV} < F_\mathrm{NUV, min}\\
            f_\mathrm{life}, & F_\mathrm{NUV} \geq F_\mathrm{NUV, min} \,\mathrm{and\, in\, HZ} \, \mathrm{for} \, \Delta t \geq \SI{100}{\mega\year}
        \end{cases}
\end{equation}
and the corresponding null hypothesis
%\begin{equation}
$H_{3, null} = f_\mathrm{life} (\theta),$
%\end{equation}
i.e., no correlation with UV flux.

@@

\section{Discussion and Conclusions}
\label{sec:discussion}
%''Which natural processes best explain how living matter spontaneously appears from nonliving matter?''~\citep{Malaterre2022}
%WE consider life ``as we know it''

@@

\subsection{Conclusions and future work}

>>>>

\subsection{Considered planets and their orbits}
All Origins of Life scenarios considered here require water as a solvent; we thus consider only rocky planets that may sustain liquid water on their surface.
Different formulations of habitable zones as regions around a star where a planet with Earth's atmospheric composition can maintain liquid water on its surface exist~\citep[e.g.,][]{MolLous2022,Spinelli2023,Tuchow2023}. CITE! Ramirez \& Kaltenegger 2017, 2018
Here, we adopt the popular estimates of \citet{Kasting1993} and \citet{Kopparapu2013,Kopparapu2014} that define a temperate zone between the runaway greenhouse transition CITE! and the maximum greenhouse limit CITE!.
We use the parametrization in \citet{Kopparapu2014} to derive luminosity and planetary mass-dependent edges of the \gls{HZ} $a_\mathrm{inner}$ and $a_\mathrm{outer}$.
We further follow \citet{Bixel2021} and classify as ``exo-Earth candidates'' all planets with radii $0.8 S^{0.25} < R < 1.4 $ that orbit within the above boundaries.
The lower limit was suggested as a minimum planet size to retain an atmosphere~\citep{Zahnle2017}.

@@

\subsection{H3: Life only originates on planets with particular UV irradiance}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions:uv}) by relating the occurrence of life on an exo-earth candidate with a minimum past quiescent stellar UV flux, focusing on the prebiotically interesting \gls{NUV} range from \SIrange{200}{280}{\nano\meter}. \todo[inline]{SUKRIT: got a good reference for this?}  %~\citep{RanjanSasselov2016}.?
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received such radiation exceeded a minimum flux $F_\mathrm{NUV, min}$.
We further require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}, and the planet to be within its momentary \gls{HZ} during this entire period.

For each exo-earth candidate, we interpolated the age- and stellar mass-dependent \gls{HZ} fluxes obtained by \citet{Richey-Yowell2023} and computed the evolution of the inner (runaway greenhouse) and outer (maximum greenhouse) edges as a function of planet mass, stellar spectral type using the results of \citet{Kopparapu2014} and the stellar luminosity evolution of \citet{Baraffe1998}.
We then determined which planets were both in the \gls{HZ} and had \gls{NUV} fluxes above $F_\mathrm{NUV, min}$ for $\Delta T_\mathrm{min} \geq \SI{100}{\mega\year}$.
We assigned the development of life to a fraction $f_\mathrm{life}$ of all temperate planets fulfilling these requirements.
For a population-level hypothesis, we then have
\begin{equation}\label{eq:hypothesis-uv}
    H_{3} = f_\mathrm{life} (\theta, F_\mathrm{NUV}) =
        \begin{cases}
            0 , & F_\mathrm{NUV} < F_\mathrm{NUV, min}\\
            f_\mathrm{life}, & F_\mathrm{NUV} \geq F_\mathrm{NUV, min} \,\mathrm{and\, in\, HZ} \, \mathrm{for} \, \Delta t \geq \SI{100}{\mega\year}
        \end{cases}
\end{equation}
and the corresponding null hypothesis
%\begin{equation}
$H_{3, null} = f_\mathrm{life} (\theta),$
%\end{equation}
i.e., no correlation with UV flux.

@@

\section{Discussion}
\label{sec:discussion}
%''Which natural processes best explain how living matter spontaneously appears from nonliving matter?''~\citep{Malaterre2022}
%WE consider life ``as we know it''

@@

\section{Conclusions and future work}
